Interactive decompositions of the life expectancy gap

### 2018-04-11 Manuscript/Abstract-DataVizDemo.Rmd
writing

source("../Code/life_expectancy_functions.R")
```

```{r load-data, echo=F, message=F, warning=F}
age_decomp_results <- read.csv("../Results2/age_decomp_results.csv")

@@

cod_decomp_results <- read.csv("../Results2/cod_decomp_results.csv")
cod_change_results <- read.csv("../Results2/cod_change_results.csv")
BlackWhite_results <- read.csv("../Results2/BlackWhite_results.csv")
dat.aggregated <- read.csv("../Data/dat_aggregated.csv")

@@

>>>>

source("./Code/life_expectancy_functions.R")
```

```{r load-data, echo=F, message=F, warning=F}
age_decomp_results <- read.csv("./Results2/age_decomp_results.csv")

@@

cod_decomp_results <- read.csv("./Results2/cod_decomp_results_cubic.csv")
cod_change_results <- read.csv("./Results2/cod_change_results_cubic.csv")
BlackWhite_results <- read.csv("./Results2/BlackWhite_results.csv")
dat.aggregated <- read.csv("./Data/dat_aggregated.csv")

@@

ly1 <- ggplotly(
  ggplot(data = temp,
         aes(y = COD_cont_yrs_mean, x = state.reorder2.n, fill = COD)) + coord_flip() +
    geom_bar(stat = "identity") + theme_minimal() + #geom_vline(aes(xintercept = 0)) +
    theme(legend.title = element_blank(),
          panel.background = element_rect(fill = "transparent", colour = NA), 
          plot.background = element_rect(fill = "transparent", colour = NA),
          legend.background = element_rect(fill = "transparent", colour = NA)) +
    ylab("Contribution to the life expectancy gap (years)") +
    xlab("") +
    scale_x_continuous(breaks = 1:length(levels(factor(temp$state.reorder2))), 
                       labels = levels(factor(temp$state.reorder2))) 
  ) 
ly1
